### 2018-05-09 Multiskalenanalyse.tex
Presentationsinitiation

\section{Multiskalenanalyse}
%
Das mathematische Äquivalent der Beschreibung eines Objektes mithilfe von Koeffizienten ist ein Vektorraum.